---
title: "Data analysis"
author: "Benny deMayo"
date: "5/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(png)
library(knitr)
library(markdown)
library(lmerTest)
library(ggthemes)
library(psych)
library(magrittr)
library(langcog)
library(tidyboot)
library(fs)
library(zipcode)
library(ggmap)
library(lubridate)

source(path(here::here(), "file_paths.R"))
```

```{r}

#takes in: directory of CDI data
#returns: df of all data in that directory ready for processing
readInWebCDI <- function(directory) {
  clean_data <- 
    directory %>% 
    map_df(~read_csv(., col_types = cols(.default = col_character()))) %>% #read in columns as a character
    mutate_at(
      .funs = ~case_when(
        str_detect(., "<") ~ 1, #get rid of entries that have 'less than' signs in them
        TRUE ~ as.numeric(.)
      ),
      .vars = vars(contains("Percentile"))
    ) %>% 
    mutate_at(
      .funs = ~as.numeric(.), #turn all the quantitative columns back into numeric
      .vars = 
       vars(
          which(colnames(.) == "benchmark age"):ncol(.), 
          contains("mother"), 
          contains("father"),
          contains("age")
        )
    ) 
    
  return(clean_data)
}
```


```{r}
#Read in data

pilot_data <- 
  readInWebCDI(prolific_data_directory) %>% # handle weird thing with Trues and falses that happened for some reason
  mutate(completed = case_when(
    stringr::str_to_lower(completed) == "true" ~ TRUE,
    stringr::str_to_lower(completed) == "false" ~ FALSE
  )) %>% 
  filter(completed == TRUE) 




```


```{r}
#Filtering functions

filterBirthweight <- function(data) {
  clean_data <- 
    data %>% 
    mutate_at(
      .vars = c("due_date_diff", "birth_weight_lb"),
      .funs = ~as.numeric(.)
    ) %>% 
    mutate_at(
      .vars = c("due_date_diff"),
      .funs = ~case_when(
        is.na(.) ~ 0, #turn non-NA's in this column into zeros
        TRUE ~ .
      )
    ) %>% 
    mutate(premature = due_date_diff >= 4 & birth_weight_lb < 5.5) %>% 
    filter(premature == FALSE)
  
  return(clean_data)
}

filterMultilingual <- function(data) {
  clean_data <- 
    data %>% 
    mutate_at(
      .vars = c("language_days_per_week", "language_hours_per_day"),
      .funs = ~as.numeric(.)
    ) %>% 
    mutate(
      language_hours_per_week = language_days_per_week * language_hours_per_day
    ) %>% 
    filter(is.na(language_hours_per_week) | language_hours_per_week <= 16)
}

filterVision <- function(data) {
  clean_data <- 
    data %>% 
    filter(
      hearing_loss_boolean != "1" | is.na(hearing_loss_boolean),
      vision_problems_boolean != "1" | is.na(vision_problems_boolean)
    )
  
  return(clean_data)
}

getCompletionInterval <- function(data) {
  clean_data <- 
    data %>% 
    mutate(
      completion_interval = lubridate::interval(created_date, last_modified),
      completion_time = completion_interval / lubridate::minutes()
    )
  
  return(clean_data)
}
```

Function to get ethnicity information into the table, and then another one to summarize it:

```{r}

#function to get Ethnicity

getEthnicities <- function(data) {
  clean_data <- 
    data %>% 
    mutate( #get rid of brackets in ethnicity column
      child_ethnicity = str_replace_all(child_ethnicity, "[^[:upper:]]", "")
    ) %>% 
    mutate(
      ethnicity_white = str_detect(child_ethnicity, "W"),
      ethnicity_black = str_detect(child_ethnicity, "B"),
      ethnicity_asian = str_detect(child_ethnicity, "A"),
      ethnicity_native = str_detect(child_ethnicity, "N"),
      ethnicity_other = str_detect(child_ethnicity, "O"),
      ethnicity_mixed = str_length(child_ethnicity) > 1
    )

  old_ethnicity_numbers <- 
   tibble(
      ethnicity = c("Asian", "Black", "Mixed", "White"),
      `2007 manual` = c(.069, .105, .063, .733)
    )
  
  clean_data <- 
    clean_data %>% 
    mutate( #get rid of brackets in ethnicity column
      child_ethnicity = str_replace_all(child_ethnicity, "[^[:upper:]]", "")
    ) %>%
    mutate(
      ethnicity = case_when(
        str_length(child_ethnicity) > 1 ~ "mixed",
        child_ethnicity != "A" & child_ethnicity != "B" & child_ethnicity != "W" ~ "other" ,
        TRUE ~ child_ethnicity
      ) %>% fct_recode(
        Asian = "A",
        Black = "B",
        Mixed = "mixed",
        White = "W",
        Other = "other"
      )
    ) %>% 
    filter(ethnicity != "") 
  
  return(clean_data)
}

getEthnicitySummary <- function(data) {
  select(subject_id, child_ethnicity, ethnicity) %>% 
  count(ethnicity)
}

```

Function to categorize participants by maternal education:

```{r}

getMaternalEd <- function(data) {
  clean_data <- 
    data %>% 
    mutate(
      maternal_ed = case_when(
        mother_education <= 11 ~ "Some high school or less",
        mother_education == 12 ~ "High school diploma",
        mother_education %in% seq.int(13, 15) ~ 
          "Some college education",
        mother_education >= 16 ~ "College diploma or more"
      )
    ) %>% 
    mutate(
    maternal_ed = fct_relevel(
      maternal_ed,
      "Some high school or less",
      "High school diploma",
      "Some college education",
      "College diploma or more"
    )
  )
}


```



```{r}
#Filtering out based on exlusionary criteria

pilot_data_filtered <- 
  pilot_data %>% 
  filterBirthweight() %>% 
  filterMultilingual() %>% 
  filterVision() %>% 
  getCompletionInterval() %>% 
  getEthnicities() %>% 
  getMaternalEd()

n_excluded <- nrow(pilot_data) - nrow(pilot_data_filtered)
```

`r n_excluded` out of `r nrow(pilot_1_data)` children were excluded on the basis of multilingual exposure, low birthweight, premature birth, or vision or hearing problems.


Looking at completion time:

```{r}

pilot_data_filtered %>% 
  ggplot(aes(completion_time)) +
  geom_histogram(binwidth = 5) +
  coord_cartesian(xlim = c(0, 60))

pilot_data_filtered %>% 
  filter(completion_time > 6 & completion_time < 60) %>% 
  ggplot(aes(completion_time, age)) +
  geom_point() +
  geom_smooth(method = "lm")


```

Looking at words produced:

```{r}
pilot_data_filtered %>% 
  ggplot(aes(`Total Produced`)) +
  geom_histogram(binwidth = 30)

pilot_data_filtered %>% 
  ggplot(aes(age, `Total Produced`, color = )) +
  geom_point() +
  geom_smooth(method = "lm")

```

Plots looking at demographic variables

```{r}
pilot_data_filtered %>% 
  ggplot(aes(ethnicity)) +
  geom_bar()

pilot_data_filtered %>% 
  ggplot(aes(maternal_ed)) +
  geom_bar()

pilot_data_filtered %>% 
  ggplot(aes(age, `Total Produced`, color = maternal_ed)) +
  geom_point() +
  geom_smooth(method = "lm")
```



```{r}
pilot_data_filtered %>% 
  ggplot(aes(age, `Total Produced Percentile-both`, color = maternal_ed)) +
  geom_point() +
  geom_smooth(method = "lm")

```


```{r}

pilot_data_filtered %>% 
  ggplot(aes(age, `Total Produced`, color = ethnicity)) +
  geom_point() +
  geom_smooth(method = "lm")

pilot_data_filtered %>% 
  ggplot(aes(age, `Total Produced Percentile-sex`, color = ethnicity)) +
  geom_point() +
  geom_smooth(method = "lm")

pilot_data_filtered %>% 
  filter(ethnicity != "Other") %>% 
  ggplot(aes(`Total Produced Percentile-sex`)) +
  geom_bar(binwidth = 8)

pilot_data_filtered %>% 
  filter(ethnicity  == "Other") %>% 
  View()


```

