\clearpage
\makeatletter
\efloat@restorefloats
\makeatother


\begin{appendix}
\section{}
\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2.2in}>{\raggedright\arraybackslash}p{1.2in}>{\raggedright\arraybackslash}p{2.2in}}
\caption{(\#tab:unnamed-chunk-22)Settings customizable by researchers when creating new studies to be run on the Web-CDI platform.}\\
\toprule
\textbf{Study setting} & \textbf{Default value} & \textbf{Notes}\\
\midrule
\endfirsthead
\caption[]{(\#tab:unnamed-chunk-22)Settings customizable by researchers when creating new studies to be run on the Web-CDI platform. \textit{(continued)}}\\
\toprule
\textbf{Study setting} & \textbf{Default value} & \textbf{Notes}\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
Study name & none & --\\
Instrument & none & --\\
Age range for study & none & Defaults based on instrument selected.\\
Number of days before study expiration & 14 & Must be between 1 and 28 days.\\
Measurement units for birth weight & Pounds and ounces & Weight can also be measured in kilograms (kg).\\
Minimum time (minutes) a parent must take to complete the study & 6 & --\\
Waiver of documentation & blank & Can be filled in by researchers to include a Waiver of Documentation for the participant to approve before proceeding to the experiment.\\
Pre-fill data for longitudinal participants? & No, do not populate any part of the form & Researchers can choose to pre-fill the background information and the vocabulary checklist.\\
Would you like to pay subjects in the form of Amazon gift cards? & No & If checked, researchers can enter gift codes to distribute to participants once they have completed the survey.\\
Do you plan on collecting only anonymous data in this study? (e.g., posting ads on social media, mass emails, etc) & No & If checked, researchers can set a limit for the maximum number of participants, as well as select an option that asks participants to verify that the information entered is accurate.\\
Would you like to show participants graphs of their data after completion? & Yes & --\\
Would you like participants to be able to share their Web-CDI results via Facebook? & No & --\\
Would you like participants to answer the confirmation questions? & No & Asks redundant demographic questions to serve as attention checks.\\
Provide redirect button at completion of study? & No & Used to redirect users to external site after form completion.\\
Capture the Prolific Id for the participant? & No & For integration with Prolific.\\
Allow participant to print their responses at end of Study? & No & --\\
End message & Standard end-of-study message & Can be changed to customize end-of-study message.\\*
\end{longtable}

\newpage

\begin{table}

\caption{(\#tab:unnamed-chunk-23)Regression output for WG comprehension measure.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrr}
\toprule
term & estimate & std.error & statistic & p.value & conf.low & conf.high & df\\
\midrule
Intercept & 122.361 & 2.427 & 50.407 & 0.000 & 117.600 & 127.123 & 1609\\
Age & 20.048 & 0.767 & 26.126 & 0.000 & 18.543 & 21.553 & 1609\\
Caregiver education: Some college & 17.361 & 8.179 & 2.123 & 0.034 & 1.319 & 33.404 & 1609\\
Caregiver education: High school or less & 21.778 & 10.935 & 1.991 & 0.047 & 0.329 & 43.227 & 1609\\
Age * Caregiver education: Some college & -1.989 & 2.261 & -0.880 & 0.379 & -6.423 & 2.445 & 1609\\
Age * Caregiver education: High school or less & -6.602 & 3.159 & -2.090 & 0.037 & -12.798 & -0.406 & 1609\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}

\caption{(\#tab:unnamed-chunk-23)Regression output for WG production measure.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrr}
\toprule
term & estimate & std.error & statistic & p.value & conf.low & conf.high & df\\
\midrule
Intercept & 29.786 & 1.332 & 22.354 & 0.000 & 27.172 & 32.399 & 1609\\
Age & 7.598 & 0.498 & 15.265 & 0.000 & 6.622 & 8.575 & 1609\\
Caregiver education: Some college & 5.626 & 4.920 & 1.144 & 0.253 & -4.024 & 15.276 & 1609\\
Caregiver education: High school or less & 20.442 & 7.693 & 2.657 & 0.008 & 5.352 & 35.532 & 1609\\
Age * Caregiver education: Some college & -1.356 & 1.327 & -1.022 & 0.307 & -3.960 & 1.248 & 1609\\
Age * Caregiver education: High school or less & -0.120 & 2.095 & -0.057 & 0.954 & -4.229 & 3.988 & 1609\\
\bottomrule
\end{tabular}}
\end{table}

\newpage

\begin{table}

\caption{(\#tab:unnamed-chunk-24)Minimum times to completion, WG measure}
\centering
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{2.2in}}
\toprule
Age in months & Minimum time to
completion (minutes)\\
\midrule
8 & 3.496\\
9 & 4.057\\
10 & 4.619\\
11 & 5.181\\
12 & 5.743\\
13 & 6.305\\
14 & 6.867\\
15 & 7.429\\
16 & 7.991\\
17 & 8.553\\
18 & 9.115\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}

\caption{(\#tab:unnamed-chunk-24)Minimum times to completion, WG measure}
\centering
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{2.2in}}
\toprule
Age in months & Minimum time to
completion (minutes)\\
\midrule
16 & 8.129\\
17 & 8.613\\
18 & 9.097\\
19 & 9.581\\
20 & 10.065\\
21 & 10.55\\
22 & 11.034\\
23 & 11.518\\
24 & 12.002\\
25 & 12.486\\
26 & 12.97\\
27 & 13.455\\
28 & 13.939\\
29 & 14.423\\
30 & 14.907\\
\bottomrule
\end{tabular}
\end{table}
\end{appendix}
