---
title             : "Web-CDI: A system for online administration of the MacArthur-Bates Communicative Development Inventories"
shorttitle        : "Web-CDI"

author: 
  - name          : "Benjamin deMayo"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Peretsman Scully Hall, Princeton, NJ 08540"
    email         : "bdemayo@princeton.edu"
  - name          : "Danielle Kellier"
    affiliation   : "2"
  - name          : "Mika Braginsky"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "4"
  - name          : "Virginia Marchman"
    affiliation   : "4"



affiliation:
  - id            : "1"
    institution   : "Princeton University"
  - id            : "2"
    institution   : "University of Pennsylvania"
  - id            : "3"
    institution   : "Massachussetts Institute of Technology"
  - id            : "4"
    institution   : "Stanford University"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["wordbank_cdi.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
library("fs")
r_refs("r-references.bib")

source(path(here::here(), "file_paths.R"))
source(functions_script)

#Read in (somewhat) preprocessed forms of the data
load(wg_unfiltered_path)
load(ws_unfiltered_path)
load(wg_filtered_path)
load(ws_filtered_path)
```


```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Current Usage of Web-CDI

```{r}
total_n <- nrow(wg_filtered) + nrow(ws_filtered)



```


We now turn to a discussion of the current usage of Web-CDI. We begin by giving an overview of all Web-CDI usage to date and show that data are consistent with prior data norming efforts (e.g., Fenson et al., 2007). We then focus on our recent data collection efforts that have aimed to increase representation of lower-SES participants.
	Researchers from 15 universities in the United States have collected over 6,000 administrations of the Web-CDI since it was launched in late 2017. We report here on `r total_n` of these administrations which satisfy exclusion criteria derived from previous norming efforts of the paper-format MB-CDI.  



## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
